---
title: "Untitled"
author: "Lucas Boyd"
date: "4/5/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(here)
library(tidyverse)
library(janitor)

```

```{r}
barrow <- read_csv(here("data", "barrow_ak.csv")) %>% 
  clean_names() %>% 
  select(-station, -name, -starts_with("wt"))
```


### 1. Describe your chosen location.
 What is it like? Urban/rural, polar/tropical, forest/desert, etc.
 What climate impacts might be important there?
 
### AVERAGES (Lucas)

```{r}

```


Refer to your answer for part 1 when choosing your metrics; why are these metrics likely to
be relevant, given the climate change impacts you expect at this location?

#### T, rank-sum, or other statistical tests

```{r}

```

### EXTREMES (Max)

```{r}

```

Refer to your answer for part 1 when choosing your metrics; why are these metrics likely to
be relevant, given the climate change impacts you expect at this location?

#### T, rank-sum, or other statistical tests

```{r}

```

### DISCUSSION
